\chapter{Lecture 3}
\section{More Gaussian Elimination! Ugh!}
\begin{problem}
~\\
\begin{tcolorbox}[colback=red!5!white,colframe=red!75!black]
Write down the solution of the following system:
    $$
\left(\begin{array}{ccc|c}
1 & 2 & 3 & 1 \\
2 & 4 & 7 & 2 \\
3 & 7 & 11 & 2
\end{array}\right)
    $$
\end{tcolorbox}
~\\
Applying Gaussian Elimination to the augmented matrix, we get:
$$
\left(\begin{array}{ccc|c}
1 & 2 & 3 & 1 \\
2 & 4 & 7 & 2 \\
3 & 7 & 11 & 2
\end{array}\right)\stackrel{R'_2=R_2-2R_1}{\sim}
\left(\begin{array}{ccc|c}
1 & 2 & 3 & 1 \\
0 & 0 & 1 & 0 \\
3 & 7 & 11 & 2
\end{array}\right)\stackrel{R_3'=R_3-3R_1}{\sim}
\left(\begin{array}{ccc|c}
1 & 2 & 3 & 1 \\
0 & 0 & 1 & 0 \\
0 & 1 & 2 & -1
\end{array}\right)
$$
Okay, we need to swap rows $2$ and $3$. Because We have a pivot in the third row. 
$$
\left(\begin{array}{ccc|c}
1 & 2 & 3 & 1 \\
0 & 0 & 1 & 0 \\
0 & 1 & 2 & -1
\end{array}\right)\stackrel{R_2\leftrightarrow R_3}{\sim}
\left(\begin{array}{ccc|c}
1 & 2 & 3 & 1 \\
0 & 1 & 2 & -1\\
0 & 0 & 1 & 0
\end{array}\right)
$$
Okay, I guess you can do the rest of the calculation [\textbf{HomeWork}]. 
$$
\left(\begin{array}{ccc|c}
1 & 2 & 3 & 1 \\
0 & 1 & 2 & -1\\
0 & 0 & 1 & 0
\end{array}\right)\sim\cdots\sim
\left(\begin{array}{ccc|c}
1 & 0 & 0 & 3 \\
0 & 1 & 0 & -1\\
0 & 0 & 1 & 0
\end{array}\right)
$$
\end{problem}
\clearpage
\section{How explicit the relations are!}
\begin{problem}
~\\
\begin{tcolorbox}[colback=red!5!white,colframe=red!75!black]
Write down the general solution of the following system:
$$
\left(\begin{array}{cccc|c}
1 & 3 & 1 &1 & 2 \\
2 & 6 & 3 &4 & 5 \\
7 & 21 & 8 &9 & 15
\end{array}\right)
    $$
\end{tcolorbox}
~\\
Okay, before we try to solve the system can you notice any relation among the columns? If you have $6/6$ vision which I haven't then you can definitely say the second column is thrice the first one. Because,
$$
\begin{pmatrix}
    3\\6\\21
\end{pmatrix}=3\begin{pmatrix}
    1\\2\\7
\end{pmatrix}
$$
To get other relation we need more vision remember gaining the third eye! We already have that!! Just apply Gaussian Elimination.
$$
\left(\begin{array}{cccc|c}
1 & 3 & 1 &1 & 2 \\
2 & 6 & 3 &4 & 5 \\
7 & 21 & 8 &9 & 15
\end{array}\right)\sim\cdots\sim 
\left(\begin{array}{cccc|c}
\text{$c_1$} & \text{$c_2$} & \text{$c_3$} & \text{$c_4$} & \\
1 & 3 & 0 & -1&1\\
0 & 0 & 1 & 2 &1\\
0 & 0 & 0 & 0 &0
\end{array}\right)
$$
Okay, now we can explicitly tell the relationship among the columns (using the pivot columns $c_1,c_3$). Like,  column two $c_2$ is thrice of column $c_1$. And column fourth was generated by $-c_1+2c_3$ combination. Because,
$$
-c_1+2c_3=-1\begin{pmatrix}
    1\\0\\0
\end{pmatrix}+2\begin{pmatrix}
    0\\1\\0
\end{pmatrix}=\begin{pmatrix}
    -1\\2\\0
\end{pmatrix}
$$
So, the relation is clear now. 
\end{problem}
\begin{extra}
    Find the general solution of the following systems:
    $$
    \left(\begin{array}{ccccc|c}
         1&2&3&4&5&-4\\
         3&7&10&13&16&-16 
    \end{array}\right),\qquad
    \left(\begin{array}{cc|c}
         1&3&0\\
         2&7&-1\\
         3&10&-1\\
         4&13&-1\\
         5&16&-1
    \end{array}\right)
    $$
\end{extra}
~\\
Remember how we define the nullifying vectors by vanishing the dependent columns of our matrix? And we see the relation of these null vector inside our general solution. 
\begin{extra}
    Find the null vectors of the following system:
    $$
    \left(\begin{array}{cccccccc}
        1&2&0&0&2&3&0&7\\
        0&0&0&1&3&4&0&8\\
        0&0&0&0&0&0&1&3\\
        0&0&0&0&0&0&0&0
    \end{array}\right)
    $$
\end{extra}
% I guess you don't need to write anything further @Zawad I am already typed L3+L4

